### 2019-09-12 2-Chapters/2-Chapter/agregation.tex
Removed raw inclusion of https://hal.inria.fr/hal-01705292

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main_semilogy____env1-4_932221613383548446.pdf}
	\caption[On a ``simple'' Bernoulli problem (semilog-$y$ scale). \Aggr{} is in bold red.]{On a ``simple'' Bernoulli problem (semilog-$y$ scale). \Aggr{} is in \textbf{bold \textcolor{red}{red}}.}
	\label{fig:25:EasyBernoulli}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main____env2-4_932221613383548446.pdf}
	\caption{On a ``harder'' Bernoulli problem, they all have similar performances, except \LearnExp, and our proposal \Aggr{} outperforms its competitors.}
	\label{fig:25:HardBernoulli}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main____env3-4_932221613383548446.pdf}
	\caption{On an ``easy'' Gaussian problem, only \Aggr{} shows reasonable performances, thanks to Bayes-UCB and Thompson sampling.}
	\label{fig:25:EasyGaussian}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main_semilogy____env4-4_932221613383548446.pdf}
	\caption{On a harder problem, mixing Bernoulli, Gaussian, Exponential arms, with 3 arms of each type with the \emph{same mean}.}
	\label{fig:25:HarderMixed}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/IEEE_WCNC_2018.git/plots/main_semilogx____env4-4_932221613383548446.pdf}
	\caption{The semilog-$x$ scale clearly shows the logarithmic growth of the regret for the best algorithms and our proposal \Aggr, even in a hard ``mixed'' problem (\emph{cf}. Figure~\ref{fig:25:HarderMixed}).}
	\label{fig:25:HarderMixed_semilogx}
\end{figure}

>>>>

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/Images/plots-aggregation/main_semilogy____env1-4_932221613383548446.pdf}
	\caption[On a ``simple'' Bernoulli problem (semilog-$y$ scale). \Aggr{} is in bold red.]{On a ``simple'' Bernoulli problem (semilog-$y$ scale). \Aggr{} is in \textbf{bold \textcolor{red}{red}}.}
	\label{fig:25:EasyBernoulli}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/Images/plots-aggregation/main____env2-4_932221613383548446.pdf}
	\caption{On a ``harder'' Bernoulli problem, they all have similar performances, except \LearnExp, and our proposal \Aggr{} outperforms its competitors.}
	\label{fig:25:HardBernoulli}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/Images/plots-aggregation/main____env3-4_932221613383548446.pdf}
	\caption{On an ``easy'' Gaussian problem, only \Aggr{} shows reasonable performances, thanks to Bayes-UCB and Thompson sampling.}
	\label{fig:25:EasyGaussian}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/Images/plots-aggregation/main_semilogy____env4-4_932221613383548446.pdf}
	\caption{On a harder problem, mixing Bernoulli, Gaussian, Exponential arms, with 3 arms of each type with the \emph{same mean}.}
	\label{fig:25:HarderMixed}
\end{figure}

\begin{figure}[h!]  % [htbp]
	\centering
	\includegraphics[width=1.09\linewidth]{2-Chapters/2-Chapter/Images/plots-aggregation/main_semilogx____env4-4_932221613383548446.pdf}
	\caption{The semilog-$x$ scale clearly shows the logarithmic growth of the regret for the best algorithms and our proposal \Aggr, even in a hard ``mixed'' problem (\emph{cf}. Figure~\ref{fig:25:HarderMixed}).}
	\label{fig:25:HarderMixed_semilogx}
\end{figure}
